---
title: "Dispersal Kernel clustering analysis for SharkRayMPA project"
author: "Vinay Udyawer"
date: "04/05/2018"
output: 
  html_document:
    toc: true
    toc_float: true 
    depth: 5
---

Script to calculate dispersal kernel metrics before conducting clustering analysis
Since we have multiple sources of data we will try and standardise the dispersal kernels we will first use maximum dispersal to construct a comparison between Fisheries mark recapture, Acoustic Telemetry and Satellite telemetry

```{r, eval=TRUE}
suppressPackageStartupMessages(library(tidyverse))

## Input data
fish <- as_tibble(read.csv("Data/Fisheries data/2018-03-16_Fisheries.csv"))
imos <- as_tibble(read.csv("Data/Acoustic data/IMOS/2018-03-16_IMOS_PassiveTelemetry.csv"))
otn <- readRDS("Data/Acoustic data/OTN/ATToutput/DispersalSummary_OTN.rds")
sat <- as_tibble(read.csv("Data/Satellite data/Dispersal Summaries/DispersalSummary_SatTags.csv"))
```

# Mapping data
```{r, eval=T}
suppressPackageStartupMessages({
  library(maps)
  library(mapdata)
  library(maptools)
  library(ggplot2)})

dat<-rbind(transmute(fish, Tag.ID=as.character(TagID), lat=rel_lat, lon=rel_lon, source="Mark Recapture"),
           transmute(imos, Tag.ID=as.character(tag_id), lat=release_latitude, lon=release_longitude, source="Passive Telemetry"),
           otn %>% filter(Common.Name %in% "blue shark") %>% group_by(Tag.ID) %>% summarize(lat=first(Release.Latitude), lon=first(Release.Longitude), source="Passive Telemetry"),
           sat %>% group_by(Tag.ID) %>% summarize(lat=first(Latitude), lon=first(Longitude), source="Satellite Telemetry"))

dat[dat$lon< -180,"lon"]<-dat[dat$lon< -180,"lon"]+360

wrld<-borders("world", fill=8, colour=NA)

# png("Tagplot.png", width=11, height=6, units="in", res=500)
ggplot() +
  wrld +
  geom_point(aes(x=lon, y=lat, colour=source), data=dat, cex=0.6) +
  theme_void() +
  theme(legend.position="top", legend.title= element_text(colour=NA))
# dev.off()
```


The displot function in the R folder produces a dispersal kernel plot with associated metrics for each curve.

```{r, eval=TRUE}
source("R/displot.R")
```

# Initial comparisons between fisheries, acoustic and satellite data

Because of the difference in temporal resolution, we will calculate dispersal kernels (gamma distribution) and associated parameters using Maximum dispersal distances. This is defined in each dataset by:

## Fisheries data

Dispersal distance between mark and final recapture.

```{r, eval=T}
## fisheries data summary
fDisp<-as_tibble(matrix(ncol=13, nrow=0, dimnames=list(c(), c("type","n","common_name","fit","mean","sd","shape","scale","quant.0.","quant.25.","quant.50.","quant.75.","quant.90."))))
for(i in 1:length(levels(as.factor(fish$common_name)))){
  disp<-displot(fish, cn=levels(as.factor(fish$common_name))[i], var="dis", dist="gamma")
  dd<-data.frame(type="mrecap",
                 n=n_distinct(fish[fish$common_name%in%levels(as.factor(fish$common_name))[i],"TagID"]),
                 disp)
  if(i %in% 1) {fDisp<-dd} else {fDisp<-rbind(fDisp, dd)}
}

fishdisp<-as_tibble(fDisp)
```

## Acoustic data

Maximal step dispersal distance

IMOS
```{r, eval=T}
## IMOS data summary
atf<-as_tibble(imos) %>% dplyr::select(-common_name) %>% rename(common_name = scientific_name)
atf<-filter(atf, !is.na(dis_max))

aDisp<-data.frame(matrix(ncol=13, nrow=0, dimnames=list(c(), c("type","n","common_name","fit","mean","sd","shape","scale","quant.0.","quant.25.","quant.50.","quant.75.","quant.90."))))
for(i in 1:length(levels(as.factor(atf$common_name)))){
  disp<-displot(atf, cn=levels(as.factor(atf$common_name))[i], var="dis_max", dist="gamma")
  dd<-data.frame(type="pass",
                 n=n_distinct(atf[atf$common_name%in%levels(as.factor(atf$common_name))[i],"tag_id"]),
                 disp)
  if(i %in% 1) {aDisp<-dd} else {aDisp<-rbind(aDisp, dd)}
}

imosdisp<-as_tibble(aDisp)
```

OTN:
```{r, eval=T}
## OTN data summary
ott<- 
  otn %>% 
  filter(Common.Name %in% "blue shark") %>% 
  group_by(Tag.ID) %>%
  summarize(common_name = first(Common.Name),
            dis_max = max(Consecutive.Dispersal, na.rm=TRUE))

oDisp<-data.frame(matrix(ncol=13, nrow=0, dimnames=list(c(), c("type","n","common_name","fit","mean","sd","shape","scale","quant.0.","quant.25.","quant.50.","quant.75.","quant.90."))))
for(i in 1:length(levels(as.factor(ott$common_name)))){
  disp<-displot(ott, cn=levels(as.factor(ott$common_name))[i], var="dis_max", dist="gamma")
  dd<-data.frame(type="pass",
                 n=n_distinct(ott[ott$common_name%in%levels(as.factor(ott$common_name))[i],"Tag.ID"]),
                 disp)
  if(i %in% 1) {oDisp<-dd} else {oDisp<-rbind(oDisp, dd)}
}

oDisp<- oDisp %>% filter(common_name == "blue shark")
oDisp$common_name<-"Prionace glauca"
otndisp<-as_tibble(oDisp)
```


## Satellite data

Maximal step dispersal distance
```{r, eval=T}
## Sattelite ATN data summary
satt<-as_tibble(sat) %>% 
  filter(!is.na(Consecutive.Dispersal)) %>%
  group_by(Tag.ID) %>% 
  summarize(common_name = first(Common.Name),
            dis_mean = mean(Consecutive.Dispersal, na.rm=TRUE),
            dis_max = max(Consecutive.Dispersal, na.rm=TRUE))

sDisp<-data.frame(matrix(ncol=13, nrow=0, dimnames=list(c(), c("type","n","common_name","fit","mean","sd","shape","scale","quant.0.","quant.25.","quant.50.","quant.75.","quant.90."))))
for(i in 1:length(levels(as.factor(satt$common_name)))){
  disp<-displot(satt, cn=levels(as.factor(satt$common_name))[i], var="dis_max", dist="gamma")
  dd<-data.frame(type="sat",
                 n=n_distinct(satt[satt$common_name%in%levels(as.factor(satt$common_name))[i],"Tag.ID"]),
                 disp)
  if(i %in% 1) {sDisp<-dd} else {sDisp<-rbind(sDisp, dd)}
}

sDisp$common_name<-c("Cetorhinus maximus", "Prionace glauca", "Alopias vulpinus",
                     "Mobula sp", "Carcharhinus galapagensis", "Somniosus microcephalus",
                     "Carcharhinus amblyrhynchos", "Carcharodon carcharias (j)", "Manta birostris",
                     "Carcharhinus longimanus","Lamna nasus","Lamna ditropis",
                     "Carcharias taurus", "Isurus oxyrinchus", "Carcharhinus falciformis",
                     "Carcharhinus albimarginatus", "Galeocerdo cuvier", "Rhincodon typus",
                     "Carcharodon carcharias")
satdisp<-as_tibble(sDisp)
```


## Combine the datasets together into a single tibble

```{r, eval=T}

MaxDisp<-rbind(fishdisp, imosdisp, otndisp, satdisp)
MaxDisp$common_name<-factor(MaxDisp$common_name, levels=sort(levels(MaxDisp$common_name)))

tab<- 
  MaxDisp %>%
  group_by(common_name, type) %>%
  summarize(num = sum(n)) %>%
  tidyr::spread(type, num) %>%
  data.frame()

tab$group<-c(rep("shark",29), rep("ray",2),
             rep("shark",8), rep("ray",4),
             rep("shark",4), rep("ray",3),
             "shark","ray",
             rep("shark",5), "ray",
             rep("shark",15), "ray",
             "shark",rep("ray",3))

tab$tot<-rowSums(tab[c("mrecap","pass","sat")], na.rm=T)
tab<-tab[with(tab, order(group,tot)),]

### Species with two or three sources of data
# Carcharhinus fitzroyensis   (MR 1,  Pass 2,   Sat 0)
# Rhizoprionodon taylori      (MR 1,  Pass 9,   Sat 0)
# Sphyrna mokarran            (MR 9,  Pass 4,   Sat 0)
# Callorhinchus milii         (MR 4,  Pass 10,  Sat 0)
# Carcharhinus amboinensis    (MR 13, Pass 3,   Sat 0)
# Squalus acanthias           (MR 16, Pass 6,   Sat 0)
# Galeocerdo cuvier           (MR 2,  Pass 37,  Sat 0)
# Carcharhinus albimarginatus (MR 0,  Pass 34,  Sat 6)
# Cephaloscyllium laticeps    (MR 1,  Pass 41,  Sat 0)
# Notorynchus cepedianus      (MR 9,  Pass 41,  Sat 0)
# Galeorhinus galeus          (MR 49, Pass 18,  Sat 0)
# Heterodontus portusjacksoni (MR 1,  Pass 99,  Sat 0)
# Carcharodon carcharias      (MR 0,  Pass 42,  Sat 89) **
# Prionace glauca             (MR 0,  Pass 56,  Sat 91) **
# Carcharhinus amblyrhynchos  (MR 0,  Pass 179, Sat 6)  **
# Carcharhinus leucas         (MR 102,Pass 111, Sat 0)  ++
# Carcharhinus limbatus       (MR 226,Pass 6,   Sat 0) 
# Carcharhinus plumbeus       (MR 169,Pass 77,  Sat 0)  ++
# Carcharhinus tilstoni       (MR 385,Pass 5,  Sat 0)
# Mustelus antarcticus        (MR 404,Pass 66,  Sat 0)
# Carcharhinus obscurus       (MR 460,Pass 86,  Sat 0)  ++
```

### Comparing between tagging methods
```{r, eval=F}
source("R/displot.R")

## Comparing between Fisheries and IMOS (First and last detection)
spp<- c("Carcharhinus leucas", "Carcharhinus plumbeus", "Carcharhinus obscurus")
imos_last<-read.csv("~/Dropbox/PostDoc/GSRI Shark MPA Project/Analysis/sharkray_lastdisp.csv")
im<-imos_last %>%
  filter(species %in% spp) %>%
  rename(vernacular = common_name,
         common_name = species)

quartz(width=6, height=6.5)
par(mfrow=c(3,1))
displot(fish, cn=spp[1], var="dis", dist="gamma", plotit=T, lcol="coral3", lab=T, bars=F, xlab="")
displot(im, cn=spp[1], var="disrel", dist="gamma", plotit=T, lcol="palegreen3", lab=F, bars=F, add=T , xlab=""); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)
displot(fish, cn=spp[2], var="dis", dist="gamma", plotit=T, lcol="coral3", lab=T, bars=F, xlab="")
displot(im, cn=spp[2], var="disrel", dist="gamma", plotit=T, lcol="palegreen3", lab=F, bars=F, add=T,  xlab=""); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)
displot(fish, cn=spp[3], var="dis", dist="gamma", plotit=T, lcol="coral3", lab=T, bars=F, xlab="Dispersal between tag release and final recapture (km)")
displot(im, cn=spp[3], var="disrel", dist="gamma", plotit=T, lcol="palegreen3", lab=F, bars=F, add=T); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)
```

```{r, eval=F}
## Comparing between Passive Telemetry and Sat telemetry (Daily dispersal)
spp<- c("Carcharodon carcharias","Prionace glauca","Carcharhinus amblyrhynchos")
dailyotn<-as_tibble(read.csv("Data/Acoustic data/OTN/ATToutput/Daily_DispersalSummary_OTN.csv")) %>%
  filter(common_name %in% "blue shark") %>% select(-mean.Daily.Velocity) %>% mutate(common_name ="Prionace glauca")
imos_dispersal <- readRDS("~/Documents/GitHub/SharkRay-Movement/Data/Acoustic data/IMOS/ATToutput/imos_dispersal.rds")
dailyimos<- as_tibble(imos_dispersal) %>%
  filter(discon > 0 & species %in% spp) %>%
  mutate(date=lubridate::date(lubridate::ymd_hms(detection_timestamp))) %>%
  group_by(date, tag_id) %>%
  summarize(Transmitter.Name = first(transmitter_id),
            common_name = first(species),
            Daily.Dispersal = sum(discon, na.rm=T)) %>%
  rename(Tag.ID = tag_id) %>% ungroup()

pass<-rbind(dailyotn, dailyimos)
satt<-as_tibble(read.csv("Data/Satellite data/Dispersal Summaries/Daily_DispersalSummary_SatTags.csv")) %>% select(-mean.Daily.Velocity) %>% filter(common_name %in% c("Blue Shark", "White Shark", "Juvenile White Shark", "Grey Reef Shark")) %>% mutate(common_name = as.character(common_name))
satt[satt$common_name%in%c("White Shark","Juvenile White Shark"),"common_name"]<-"Carcharodon carcharias"
satt[satt$common_name%in%"Blue Shark","common_name"]<-"Prionace glauca"
satt[satt$common_name%in%"Grey Reef Shark","common_name"]<-"Carcharhinus amblyrhynchos"

quartz(width=6, height=6.5)
par(mfrow=c(3,1))
displot(pass, cn=spp[1], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="palegreen3", lab=T, bars=F, xlab="")
displot(satt, cn=spp[1], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="steelblue3", lab=F, bars=F, add=T , xlab=""); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)
displot(pass, cn=spp[2], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="palegreen3", lab=T, bars=F, xlab="", ylim=c(0,0.4))
displot(satt, cn=spp[2], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="steelblue3", lab=F, bars=F, add=T , xlab=""); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)
displot(pass, cn=spp[3], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="palegreen3", lab=T, bars=F, xlab="Maximum Daily Dispersal (km)")
displot(satt, cn=spp[3], var="Daily.Dispersal", dist="gamma", plotit=T, lcol="steelblue3", lab=F, bars=F, add=T , xlab=""); axis(1, at=log(2.26+1), tck=1, label=F, lty=3, lwd=2)


```


```{r, eval=F}
## Trial joyplots ** Did not work **
library(ggridges)

for(i in 1:nrow(MaxDisp)){
 if(i %in% 1){res<-data.frame(common_name=MaxDisp$common_name[i],
                              type=MaxDisp$type[i],
                              mean=MaxDisp$mean[i],
                              xx=dgamma(log(seq(0,5,length=100)+1), scale=MaxDisp$scale[i], shape=MaxDisp$shape[i]))}
  else{
     res<-rbind(res, data.frame(common_name=MaxDisp$common_name[i],
                              type=MaxDisp$type[i],
                              mean=MaxDisp$mean[i],
                              xx=dgamma(log(seq(0,5,length=100)+1), scale=MaxDisp$scale[i], shape=MaxDisp$shape[i])))}
  }

as_tibble(res)

ggplot(res, aes(x=xx, y=common_name)) +
  geom_density_ridges() +
  theme_ridges()

```

## Species breakdown

```{r, eval=T}

# quartz(height=6.5, width=8); 
par(mar=c(4.5,14,0,1), mfrow=c(1,3))

dat<- tab %>% filter(!is.na(mrecap)) %>% arrange(group, mrecap)
barplot(dat$mrecap, names.arg=dat$common_name, horiz=T, las=1, border=NA, col="steelblue2", 
        cex.names=0.9, font=4, xaxt="n", xlab="Number of individuals tagged", xlim=c(0,500))
axis(1)
dat<- tab %>% filter(!is.na(pass)) %>% arrange(group, pass)
barplot(dat$pass, names.arg=dat$common_name, horiz=T, las=1, border=NA, 
        col=c("coral","steelblue2")[as.factor(dat$group)], cex.names=0.9, font=4, xaxt="n", 
        xlab="Number of individuals tagged", xlim=c(0,200))
axis(1)
dat<- tab %>% filter(!is.na(sat)) %>% arrange(group, sat)
barplot(dat$sat, names.arg=dat$common_name, horiz=T, las=1, border=NA, 
        col=c("coral","steelblue2")[as.factor(dat$group)], cex.names=0.9, font=4, xaxt="n", 
        xlab="Number of individuals tagged", xlim=c(0,150))
axis(1)

```



# Cluster Analysis

Since we passive telemetry is the largest dataset we will use that to conduct a cluster analysis

```{r, eval = T}
suppressPackageStartupMessages({
  library(cluster)
  library(factoextra)
  library(NbClust)
  library(dendextend)
  library(circlize)
  library(viridis)})

## Data preperation (Species level)
dat<-rbind(oDisp, aDisp)
pp<-
  dat %>%
  filter(type %in% "pass") %>%
  na.omit() %>%
  data.frame()
rownames(pp)<-pp$common_name
scalepp<-scale(pp[,5:13])

# ## individual level
# pp<- as_tibble(imos_dispersal) %>%
#   filter(discon > 0) %>%
#   # mutate(date=lubridate::date(lubridate::ymd_hms(detection_timestamp))) %>%
#   group_by(tag_id) %>%
#   summarize(Transmitter.Name = first(transmitter_id),
#             common_name = first(species),
#             Max.Dispersal = max(discon, na.rm=T)) %>%
#   ungroup() %>%
#   data.frame()
# rownames(pp)<-pp$tag_id
# scalepp<-pp$Max.Dispersal

## Identifying ideal number of clusters
nb <- NbClust(scalepp, distance = "euclidean", min.nc = 2,
        max.nc = 10, method = "ward.D")
## 4 clusters (Species level)

## Hierarchichal clustering
ppHclust<-hclust(dist(scalepp, method = "euclidean"), method = "complete")
# dend <- as.dendrogram(ppHclust)
# dend <- dend %>% 
#   color_branches(k=5) %>% 
#   color_labels(k=5)
# circlize_dendrogram(dend, labels_track_height = 0.1, dend_track_height = 0.85, cex=0.1)


fviz_dend(ppHclust, k = 4, 
          cex = 0.4,
          k_colors = c("#2E9FDF", "#00AFBB", "#E7B800", "#FC4E07"),
          color_labels_by_k = TRUE, 
          rect = TRUE,
          main=""
          )



```




















