---
title: "Activity Space Scaling"
author: "C Mull"
date: "May 2, 2018"
output: html_document
---

#Scaling of Shark and Ray Movement Metrics

```{r load packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(phytools)
library(MCMCglmm)
library(brms)
library(diversitree)
library(treeplyr)
```

##Data Loading and Summary
Currently this is working with the IMOS acoustic tracking data and the measures of cumulative activity space for each individual. We will be looking at AS for all individuals, the distribution across size classes, and the species means.

```{r load activity space data and tree and color scales, echo=FALSE, message=FALSE, warning=FALSE}
#for some reason knitr needs me to set the working directory now
#setwd("/Users/cmull/Dropbox/Work/Postdoc SFU/Data and Analysis/R") #THIS ONLY NEEDS TO BE RUN WHEN KNITTING
#load data
act.sp <- read.csv("Data/ActivitySpace.Trait.csv", header = T)
#markrecap <- read.csv("Data/2018-03-16_Fisheries.csv", header = T)

#Generate activity space in square kilometers and mass estimates for life stages
act.sp <- act.sp %>%
  mutate(mcp.km = mcp/1000000,
         bbk50.km = bbk50/1000000,
         bbk95.km = bbk95/1000000,
         mass.mat = (size.at.mat^length.weight.b)*length.weight.a,
         max.mass = (max.size^length.weight.b)*length.weight.a,
         pup.mass = (pup.size^length.weight.b)*length.weight.a) %>%
  group_by(G.species) %>% mutate(count = n()) #add a count column to filter out species with less than 10 individuals tagged

#load tree
tree <- read.nexus("Data/trees/10cal.tree250.nex")
```

```{r species mean activity space, echo=FALSE, message=FALSE, warning=FALSE}
#generate species means for each variable. For values that are all the same (e.g. taxonomy) use first() to grab the first value. For continuous values (e.g. mcp) use na.exclude() otherwise NAs will cause it to fail.
act.sp.mean<-act.sp %>%
                group_by(G.species) %>%
                summarise(species.id = first(G.species),
                          n = length(mcp),
                          subclass = first (subclass),
                          order = first(order),
                          mcp = mean(na.exclude(mcp)),
                          mcp.km = mean(na.exclude(mcp.km)),
                          bbk50 = mean(na.exclude(bbk50)),
                          bbk90 = mean(na.exclude(bbk95)),
                          days_det = mean(days_det),
                          dis_max = mean(na.exclude(dis_max)),
                          TL.mean = mean(na.omit(Length_cm)),
                          body.mass = mean(na.omit(body.mass.kg)),
                          habitat = first(habitat),
                          range.depth = max(range.depth),
                          range.lat = max(range.lat),
                          area = max(area),
                          Trophic.group = first(Trophic.group),
                          size.at.mat = max(size.at.mat),
                          max.size = max(max.size),
                          k = max(k),
                          age.mat = max(age.mat),
                          max.age = max(max.age),
                          bearing.mode = first(bearing.mode),
                          breeding.interval = max(breeding.interval),
                          ecomorphotype = first(ecomorphotype),
                          lifestyle = first(lifestyle),
                          ecomorph.life = first(ecomorph.life),
                          Red.List = first(Red.List.status.new),
                          ED = max(median.ED))

act.sp.mean <- filter(act.sp.mean, !is.na(mcp.km)) #Just to clean up the dataframe for future plotting.
act.sp.mean <- filter(act.sp.mean, !is.na(body.mass))
```

##Model Comparison with GLMM

This will be a first run of model comparison that does not account for phylogeny directly, but can taxonomy can be accounted for.

```{r}
as.lm_A <- glm(log10(bbk95)~log10(body.mass.kg), data = act.sp)
summary(as.lm_A)

#with phylogenetic correction
dat.phy <- treeplyr::make.treedata(tree, act.sp.mean, name_column = "G.species")

mean.tree <- dat.phy$phy
mean.dat <- dat.phy$dat

library(nlme)

AS.mean.phy <- gls(log10(mcp.km)~log10(body.mass.kg), data = na.omit(act.sp), correlation = corPagel(1,tree), method = "ML")
```


## Model Comparison with brms

 To examine the full Activity Space dataset we will need to perform a repeated measures pGLMM model using brms on our suite of candidate models including: body mass, lifestyle, habitat type, and trophic guild. 
 
###Using MCP in Km^2

```{r AS-MCP, eval=FALSE, echo=FALSE}
#create the covariance matrix for adding to the phylogenetic mixed model
A <- ape::vcv.phylo(tree)

#create a list or priors to apply across all models. These are uninformative.
priors.AS <- c(prior(normal(0, 10), "b"),
    prior(normal(0, 50), "Intercept"),
    prior(student_t(3, 0, 20), "sd"),
    prior(student_t(3, 0, 20), "sigma"))

#Model A: a simple model looking at activity space over body mass
actsp_mcp_A <- brm(
  log10(mcp.km) ~ log10(body.mass.kg) + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_A <- add_ic(actsp_mcp_A, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_A, file="R/Model Outputs/bbk50/test.rds")
actsp_mcp_A <- readRDS("Model Outputs/actsp_mcp_A_190713.rds")

#Model B1: activity space over body mass with lifestyle as a cactor
actsp_mcp_B1 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg) + lifestyle + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_B1 <- add_ic(actsp_mcp_B1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_B1, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_B1_190713.rds")
actsp_mcp_B1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_B1_190713.rds")

#Model B2: activity space over body mass with an interaction with lifestyle
actsp_mcp_B2 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg)*lifestyle + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_B2 <- add_ic(actsp_mcp_B2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_B2, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_B2_190713.rds")
actsp_mcp_B2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_B2_190713.rds")

#Model C1: activity space over body mass with habitat as a cofactor
actsp_mcp_C1 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg) + habitat2 + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_C1 <- add_ic(actsp_mcp_C1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_C1, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_C1_190713.rds")
actsp_mcp_C1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_C1_190713.rds")

#Model C2: activity space over body mass with an interaction with habitat
actsp_mcp_C2 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg)*habitat2 + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_C2 <- add_ic(actsp_mcp_C2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_C2, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_C2_190713.rds")
actsp_mcp_C2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_C2_190713.rds")

#Model D1: Body mass with Trophic Guild as a cofactor
actsp_mcp_D1 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg) + Trophic.group + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_D1 <- add_ic(actsp_mcp_D1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_D1, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_D1_190713.rds")
actsp_mcp_D1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_D1_190713.rds")

#Model D2: Activity space over body mass with 
actsp_mcp_D2 <- brm(
  log10(mcp.km) ~ log10(body.mass.kg)*Trophic.group + (1|G.species), data = act.sp, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_mcp_D2 <- add_ic(actsp_mcp_D2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_mcp_D2, file="~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_D2_190713.rds")
actsp_mcp_D2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_mcp_D2_190713.rds")

#Compare model WAIC values to assess model support
loo.mcp <- loo(actsp_mcp_A, actsp_mcp_B1, actsp_mcp_B2, actsp_mcp_C1, actsp_mcp_C2, actsp_mcp_D1, actsp_mcp_D2, "waic")
```

###Using bbk50 in Km^2

```{r AS-bbk50, eval=FALSE, echo=FALSE}
#create the covariance matrix for adding to the phylogenetic mixed model
A <- ape::vcv.phylo(tree)

#create a list or priors to apply across all models. These are uninformative.
priors.AS <- c(prior(normal(0, 10), "b"),
    prior(normal(0, 50), "Intercept"),
    prior(student_t(3, 0, 20), "sd"),
    prior(student_t(3, 0, 20), "sigma"))

#Model A: a simple model looking at activity space over body mass
actsp_bbk50_A <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg) + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_A <- add_ic(actsp_bbk50_A, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_A, file="R/Model Outputs/bbk50/actsp_bbk50_A_190714.rds")
#actsp_bbk50_A <- readRDS("Model Outputs/actsp_bbk50_A_190713.rds")

#Model B1: activity space over body mass with lifestyle as a cactor
actsp_bbk50_B1 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg) + lifestyle + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_B1 <- add_ic(actsp_bbk50_B1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_B1, file="R/Model Outputs/bbk50/actsp_bbk50_B1_190714.rds")
#actsp_bbk50_B1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_B1_190713.rds")

#Model B2: activity space over body mass with an interaction with lifestyle
actsp_bbk50_B2 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg)*lifestyle + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_B2 <- add_ic(actsp_bbk50_B2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_B2, file="R/Model Outputs/bbk50/actsp_bbk50_B2_190714.rds")
#actsp_bbk50_B2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_B2_190713.rds")

#Model C1: activity space over body mass with habitat as a cofactor
actsp_bbk50_C1 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg) + habitat2 + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_C1 <- add_ic(actsp_bbk50_C1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_C1, file="R/Model Outputs/bbk50/actsp_bbk50_C1_190714.rds")
#actsp_bbk50_C1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_C1_190713.rds")

#Model C2: activity space over body mass with an interaction with habitat
actsp_bbk50_C2 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg)*habitat2 + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_C2 <- add_ic(actsp_bbk50_C2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_C2, file="R/Model Outputs/bbk50/actsp_bbk50_C2_190714.rds")
#actsp_bbk50_C2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_C2_190713.rds")

#Model D1: Body mass with Trophic Guild as a cofactor
actsp_bbk50_D1 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg) + Trophic.group + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_D1 <- add_ic(actsp_bbk50_D1, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_D1, file="R/Model Outputs/bbk50/actsp_bbk50_D1_190714.rds")
#actsp_bbk50_D1 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_D1_190713.rds")

#Model D2: Activity space over body mass with 
actsp_bbk50_D2 <- brm(
  log10(bbk50.km) ~ log10(body.mass.kg)*Trophic.group + (1|G.species), data = act.sp.no, 
  family = gaussian(), cov_ranef = list(phylo = A), iter = 10000,
  control = list(adapt_delta = 0.99),#the adapt_delta is set close to 1 (bound from 0.8-1) to reduce the divergences
  prior = priors.AS,
  save_all_pars = TRUE)
actsp_bbk50_D2 <- add_ic(actsp_bbk50_D2, ic=c("waic", "R2", "marglik")) #add IC to model fit for comparison
saveRDS(actsp_bbk50_D2, file="R/Model Outputs/bbk50/actsp_bbk50_D2_190714.rds")
#actsp_bbk50_D2 <- readRDS("~/Dropbox/Work/Postdoc SFU/Data and Analysis/R/R/Model Outputs/actsp_bbk50_D2_190713.rds")

#Compare model WAIC values to assess model support
loo.bbk <- loo(actsp_bbk50_A, actsp_bbk50_B1, actsp_bbk50_B2, actsp_bbk50_C1, actsp_bbk50_C2, actsp_bbk50_D1, actsp_bbk50_D2, "waic")
loo.bbk
saveRDS(loo.bbk, file="R/Model Outputs/bbk50/loo.bbk_190714.rds")
```

Check out the summary and output

```{r summaries, echo=FALSE}
summary(actsp_A)
summary(actsp_B1)
summary(actsp_B2)
summary(actsp_C1)
summary(actsp_C2)
summary(actsp_D1)
summar(actsp_D2)

actsp_A$waic
actsp_B1$waic
actsp_B2$waic
actsp_C1$waic
actsp_C2$waic
actsp_D1$waic
actsp_D2$waic

```

##Plotting
```{r setting plotting parameters and colors, echo=FALSE}
#Setting Colour scales and themes for plotting
col.subclass <- scales::alpha(c("red", "green", "blue"), 0.5)
names(col.subclass) <- levels(act.sp$subclass)
col.tax <- scale_colour_manual(name = "subclass", values = col.subclass)

col.hab <- scales::alpha(c("red", "blue"), 0.5)
names(col.hab) <- levels(act.sp$Habitat)
col.habitat <- scale_colour_manual(name = "Habitat", values = col.hab)

col.hab.new <- scales::alpha(c("red", "yellow", "blue", "green"), 0.5)
names(col.hab.new) <- levels(act.sp$habitat)
col.habitat.new <- scale_colour_manual(name = "habitat.new", values = col.hab.new)

col.trophic <- scales::alpha(c("blue", "royalblue", "skyblue", "navy"), 0.5)
names(col.trophic) <- levels(act.sp$Trophic.group)
col.feed <- scale_colour_manual(name= "Trophic.group", values = col.trophic)

col.lifestyle <- scales::alpha(c("red","blue"), 0.5)
names(col.lifestyle) <- levels(act.sp$lifestyle)
col.life <- scale_colour_manual(name="lifestyle", values = col.lifestyle)

col.ecomorph.life <- scales::alpha(c("darkblue", "yellow", "darkgreen", "lightgreen", "lightblue", "darkred", "red"), 0.75)
names(col.ecomorph.life) <- levels(act.sp$ecomorph.life)
col.ecolife <- scale_colour_manual(name="ecomorph.life", values = col.ecomorph.life)

#loading ggplot2 talk theme (transparent bkg with grey/white)
source("R/Talk_theme_ggplot.R")
source("R/Paper_theme_ggplot.R")
```

###Exploratory Plots
First will be data summaries. Look at the size distribution within each species. 

####Mean AS scaling between species
```{r mean activity space plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
AS.mean.plot <- ggplot(subset(act.sp.mean, !is.na(mcp.km)), aes(body.mass, mcp.km)) + 
  geom_point(size=5, color = scales::alpha('grey50', 0.5)) +
  scale_x_log10() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm, colour = "grey80") + 
  theme_talk() #NOTE to change things like text size in the plot you need to change the theme file and then reload
AS.mean.plot

pdf("Plots/mean.actsp.scaling.pdf", width = 10, height = 8)
AS.mean.plot
dev.off()
```

```{r mean activity space plot by lifestyle, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
AS.mean.life.plot <- ggplot(subset(act.sp.mean, !is.na(mcp.km)), aes(body.mass, mcp.km, colour=lifestyle)) + 
  geom_point(size=5) +
  scale_x_log10() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  col.life +
  geom_smooth(method = lm, aes(fill=lifestyle)) +
  theme_talk()
AS.mean.life.plot

pdf("Plots/AS.mean.lifstyle.pdf", width = 10, height = 8)
AS.mean.life.plot
dev.off()
```

```{r mean activity space plot by taxonomy, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
AS.mean.tax.plot <- ggplot(subset(act.sp.mean, !is.na(mcp.km)), aes(body.mass, mcp.km, colour = subclass)) + 
  geom_point(aes(size=5)) +
  col.tax +
  scale_x_log10() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm, aes(fill=subclass)) +
  theme_talk()
AS.mean.tax.plot

pdf("Plots/AS.mean.subclass.plot.pdf", width = 10, height = 8)
AS.mean.tax.plot
dev.off()
```

```{r mean activity space plot by trophic group, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
AS.mean.trophic.plot <- ggplot(subset(act.sp.mean, !is.na(mcp.km)), aes(body.mass, mcp.km, colour = Trophic.group)) + 
  geom_point(aes(size=10)) +
  scale_x_log10() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) +
  col.feed +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm) +
  theme_talk()
AS.mean.trophic.plot

pdf("Plots/AS.mean.Trophic.plot.pdf", width = 10, height = 8)
AS.mean.trophic.plot
dev.off()
```

```{r multiplanel plot for the species means plotsecho=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
#This is a simple mulipanel plot for SCF reporting purposes. Not paper figure quality...
Rmisc::multiplot(AS.mean.plot, AS.mean.tax.plot, AS.mean.life.plot, AS.mean.trophic.plot, cols = 2)
```

####Individual AS within species

To be more informative filter out all the species for which there are less than 10 tagged individuals. Vertical lines represent size at birth, maturity, and maximum size.

```{r size.distribution, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
as.filt <- filter(act.sp, count>10, G.species !="Rhincodon_typus")
tag.size.dist <- ggplot(as.filt, aes(x=Length_cm)) +
  geom_histogram(binwidth=10, aes(y=..density..),colour="black",fill="grey75") + 
  geom_density(aes(y=..density..)) +
  geom_vline(aes(xintercept = pup.size), linetype=2, color = "red") +
  geom_vline(aes(xintercept = size.at.mat), linetype=2, color = "grey50") +
  geom_vline(aes(xintercept = max.size), linetype=2, color = "red") +
  facet_wrap(~G.species, scales = "free_y") #+
  #theme_talk()

tag.size.dist

pdf("Plots/tag.size.dist.pdf", width = 12, height = 10)
tag.size.dist
dev.off()

```

Look at the distribution of activity space across species. This will need to be fixed to generate Activity Space Kernels...similar to Vinay's dispersal kernel work.

#```{r activity.space.distribution, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
#ggplot(subset(as.filt, !is.na(mcp.km)), aes(x=mcp.km)) +
#  geom_histogram(binwidth=100, aes(y=..density..),colour="black",fill="grey75") + 
#  geom_density(aes(y=..density..)) +
#  facet_wrap(~G.species, scales = "free_y")
#```

Look at AS scaling witin each species
```{r}
facet.AS.scaling <- ggplot(subset(as.filt, !is.na(mcp.km)), aes(body.mass.kg, mcp.km, colour = ecomorph.life)) +
  geom_point(size=2.5, color = scales::alpha('grey50', 0.5)) +
  #col.ecolife +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks(colour = "grey50") +
  #geom_smooth(method=lm, se=F) +
  facet_wrap(~G.species) #+
  #theme_talk()
facet.AS.scaling

pdf("Plots/facet.AS.pdf", width = 12, height = 8)
facet.AS.scaling
dev.off()

```


```{r individual activity space by lifestyle, echo=FALSE, fig.height=10, fig.width=10, message=F, warning=FALSE}
AS.life.plot <- ggplot(subset(act.sp, !is.na(mcp.km)), aes(body.mass.kg, mcp.km, colour=lifestyle)) + 
  geom_point(size=7.5) +
  scale_x_log10() +
  scale_y_log10() +
  annotation_logticks(colour = "grey50") +
  col.life +
  geom_smooth(method = lm, aes(fill=lifestyle)) +
  theme_talk()
AS.life.plot

pdf("Plots/AS.lifstyle.pdf", width = 10, height = 8)
AS.life.plot
dev.off()
```

```{r dispersal distance saturation plot, echo=FALSE}

plot(log10(disp$dis_max)~disp$days.at.liberty, col=as.factor(disp$tag.type))

disp <- read.csv("Data/Dispersal.Trait.csv", header = T)

col.tag <- scales::alpha(c("red", "green", "blue"), 0.5)
names(col.tag) <- levels(disp$tag.type)
color.tag <- scale_colour_manual(name = "tag.type", values = col.tag)

disp <- filter(disp, days.at.liberty>0)

Disp.plot <- ggplot(subset(disp, !is.na(dis_max)), aes(days.at.liberty, dis_max, colour = tag.type)) + 
  geom_point(aes(size=10)) +
  #scale_x_log10() +
  scale_y_log10(labels = function(x) format(x, scientific = FALSE)) +
  color.tag +
  theme_talk()
Disp.plot

pdf("Plots/dispersal.time.pdf", width = 10, height = 8)
Disp.plot
dev.off()
```

```{r plot by ecomorpholife, echo=FALSE}

```

```{r example species plots, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
#subset Carcharhinus amblyrhynchos which doesn't show strong scaling
Cambly <- filter(act.sp, G.species == "Carcharhinus_amblyrhynchos", Length_cm>0)

AS.Cambly <- ggplot(subset(Cambly, !is.na(mcp.km)), aes(body.mass.kg, mcp.km)) + 
  geom_point(size=7.5, color = scales::alpha('grey50', 0.5)) +
  scale_x_log10() +
  scale_y_log10() + #labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm, colour="grey80") +
  theme_talk()
AS.Cambly

pdf("Plots/C.amblyrhynchos.scaling.pdf", width = 10, height = 8)
AS.Cambly
dev.off()

#subset Negaprion acutidens which shows clear scaling
Negaprion <- filter(act.sp, G.species == "Negaprion_acutidens", Length_cm>0)

AS.Negaprion <- ggplot(subset(Negaprion, !is.na(mcp.km)), aes(body.mass.kg, mcp.km)) + 
  geom_point(size=7.5, color = scales::alpha('grey50', 0.5)) +
  scale_x_log10() +
  scale_y_log10() + #labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm, colour="grey80") +
  theme_talk()
AS.Negaprion

pdf("Plots/N.acutidens.scaling.pdf", width = 10, height = 8)
AS.Negaprion
dev.off()

#Carcharhinus melanopterus
Melanopterus <- filter(act.sp, G.species == "Carcharhinus_melanopterus", Length_cm>0)

AS.Melanopterus <- ggplot(subset(Melanopterus, !is.na(mcp.km)), aes(body.mass.kg, mcp.km)) + 
  geom_point(size=7.5, color = scales::alpha('grey50', 0.5)) +
  scale_x_log10() +
  scale_y_log10() + #labels = function(x) format(x, scientific = FALSE)) +
  annotation_logticks(colour = "grey50") +
  geom_smooth(method = lm, colour="grey80") +
  theme_talk()
AS.Melanopterus

pdf("Plots/C.melanopterus.scaling.pdf", width = 10, height = 8)
AS.Melanopterus
dev.off()

```
